WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2019-03-06 review/referee_response_0.txt

The authors present a number of new and high-quality transit observations of
the hot Jupiter WASP-4b observed by TESS. After comparing the predicted
mid-transit times (obtained only considering the pre-existing transits in the
literature) with the measured values from the TESS light curves, the authors
conclude that the TESS transits occur ~ 82 seconds earlier than predicted. They
examine different possibilities and find that the 2 most favored scenarios to
explain this deviation are orbital decay and apsidal precession. However, the
authors caution that more observations are needed to confirm these results.
Also, they redetermine various parameters of the system, finding them in
general agreement with literature values.

In general, the manuscript is scientifically accurate and the results presented
in it certainly will be of interest to other investigators in the field. Then,
I consider this paper worthy of being published after the concerns described
below be addressed.

Below are my comments, beginning with the major points. I recommend the authors
take them into consideration when revising their manuscript.

  > RESPONSE: We thank the referee for this summary. In our revision,
  > we have added weight to a third possible explanation that we
  > previously mentioned but did not sufficiently emphasize: a massive
  > outer companion, perhaps on an eccentric orbit, might be able to
  > explain both the transit and radial velocity observations. We have
  > described this possibility throughout the text where appropriate.
  > We also added our own re-analysis of the extant RV data (now
  > section 4.3, and figure 6) to check on the Knutson et al (2014)
  > result that the star's acceleration towards our line of sight is
  > only weakly detected, and is an order of magnitude too small to
  > explain the observed period derivative from the transit times.

@@

2. NEW TRANSITS AND SYSTEM PARAMETERS:

Section 2.1:

i) It could be informative to provide a reference for the "Deep Space Network".

  > RESPONSE: We are not aware of any paper that suits the purpose
  > here, so we added a citation to the URL of the Deep Space Network.

### 2019-03-06 paper/ms.tex
update gitignore

WASP-4 was observed by TESS with Camera 2 from August 23 to September
20, 2018, within the second ``sector'' of science operations.  The
star is designated as TIC 402026209 in the TESS Input Catalog
\citep{stassun_TIC_2018}.  The pixel data for an $11\times11$ array
surrounding WASP-4 were averaged into 2-minute stacks by the onboard
computer.  The data were downlinked via the Deep Space
Network\footnote{\url{https://deepspace.jpl.nasa.gov}}, and the
spacecraft timestamps were calibrated against the ground-station
clocks.  The spacecraft clock times were then transformed by the
Payload Operations Center into the {\it Temps Dynamique Barycentrique}
(TDB) reference system.  The images were then reduced to lightcurves
by the Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  During this processing, the SPOC used
the known spacecraft trajectory to compute the barycentric time
corrections on a target by target basis, and expressed the timestamps
as Barycentric TESS Julian Dates (BTJD), which is simply the
\replaced{b}{B}arycentric Julian \replaced{d}{D}ate minus
2{,}457{,}000.  Lightcurves that were flagged \deleted{as Threshold
Crossing Events} by the SPOC pipeline \added{as crossing a transit
detection threshold} were then vetted and released by the MIT TESS
Science Office to the Mikulski Archive for Space Telescopes on
November 29, 2018~\citep{ricker_tess_alerts_2018}.

@@

Figure~\ref{fig:lightcurves} shows the lightcurve of each individual
transit, the best-fit models, and the residuals.  Table~2 reports the
mid-transit times and their uncertainties.  After binning the
residuals to 1-hour windows, the lightcurves have an rms scatter of
586\,{\rm ppm}.  The pre-launch TESS noise
model\footnote{\url{github.com/lgbouma/tnm}}
(\citealt{winn_photonflux_2013}, \citealt{Sullivan_2015} Section 6.4)
would have predicted an error budget consisting of the following terms
added in quadrature: 410\,{\rm ppm} from photon-counting noise,
202\,{\rm ppm} from detector read noise, and 673\,{\rm ppm} from the
zodiacal background light.  The level of background light appears to
have been overestimated in the model.

@@

\acknowledgements
L.G.B.\ and J.N.W.\ gladly acknowledge helpful discussions with
A.~Bailey, F.~Dai, J.~Goodman, K.~Patra and V.~Van Eylen, and are
grateful to the people who have turned TESS from an idea into reality.
\added{L.G.B. thanks A.~Bixel and E.~May for clarifying details
concerning the available IMACS lightcurves.}
%
WASP-4 was included on the ``short-cadence'' target list thanks to the
Guest Investigator programs of J.\ Southworth and S.\ Kane (G011112
and G011183 respectively). 
%
J.N.W.\ thanks the TESS project and the Heising-Simons foundation for
supporting this work.
%
T.D. acknowledges support from MIT's Kavli Institute as a Kavli
postdoctoral fellow.
%
J.M.D. acknowledges funding from the European Research Council (ERC)
under the European Union's Horizon 2020 research and innovation
programme (grant agreement no. 679633; Exo-Atmos), and support from
the NWO TOP Grant Module 2 (Project Number 614.001.601).
%
J.E.R. was supported by the Harvard Future Faculty Leaders
Postdoctoral fellowship.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} 
  \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{radvel} \citep{fulton_radvel_2018},
  \texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
}

@@

We repeated all the data reduction and analysis steps described in
this paper for other hot Jupiters observed by TESS for which timing
data exists spanning many years.  First, we checked which hot Jupiters
were observed over the first three TESS sectors using a combination of
\texttt{tessmaps}\footnote{\url{github.com/lgbouma/tessmaps}} and
TEPCat \citep{southworth_homogeneous_2011}.  We recalculated the
barycentric corrections using the \citet{eastman_achieving_2010} code,
and found values that agreed with the lightcurve headers to within
about 1 second.  We then selected hot Jupiters for which there were at
least five distinct epochs reported in the peer-reviewed literature.
We required that each observation be of a single transit, that the
midpoint be fit as a free parameter, and that the time system be
clearly documented.  Our final hot Jupiter sample included WASP-4b,
5b, 6b, 18b, and 46b.  The collected and measured times are given in
Tables~5, 6, 7, and 8 for each.

>>>>

WASP-4 was observed by TESS with Camera 2 from August 23 to September
20, 2018, within the second ``sector'' of science operations.  The
star is designated as TIC 402026209 in the TESS Input Catalog
\citep{stassun_TIC_2018}.  The pixel data for an $11\times11$ array
surrounding WASP-4 were averaged into 2-minute stacks by the onboard
computer.  The data were downlinked via the Deep Space
Network\footnote{\url{deepspace.jpl.nasa.gov}}, and the
spacecraft timestamps were calibrated against the ground-station
clocks.  The spacecraft clock times were then transformed by the
Payload Operations Center into the {\it Temps Dynamique Barycentrique}
(TDB) reference system.  The images were then reduced to lightcurves
by the Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  During this processing, the SPOC used
the known spacecraft trajectory to compute the barycentric time
corrections on a target by target basis, and expressed the timestamps
as Barycentric TESS Julian Dates (BTJD), which is simply the
\replaced{b}{B}arycentric Julian \replaced{d}{D}ate minus
2{,}457{,}000.  Lightcurves that were flagged \deleted{as Threshold
Crossing Events} by the SPOC pipeline \added{as crossing a transit
detection threshold} were then vetted and released by the MIT TESS
Science Office to the Mikulski Archive for Space Telescopes on
November 29, 2018~\citep{ricker_tess_alerts_2018}.

@@

Figure~\ref{fig:lightcurves} shows the lightcurve of each individual
transit, the best-fit models, and the residuals.  Table~2 reports the
mid-transit times and their uncertainties.  After binning the
residuals to 1-hour windows, the lightcurves have an rms scatter of
586\,{\rm ppm}.  The pre-launch TESS noise
model\footnote{\url{github.com/lgbouma/tnm}, commit \texttt{be06f09}}
(\citealt{winn_photonflux_2013}, \citealt{Sullivan_2015} Section 6.4)
would have predicted an error budget consisting of the following terms
added in quadrature: 410\,{\rm ppm} from photon-counting noise,
202\,{\rm ppm} from detector read noise, and 673\,{\rm ppm} from the
zodiacal background light.  The level of background light appears to
have been overestimated in the model.

@@

\acknowledgements
L.G.B.\ and J.N.W.\ gladly acknowledge helpful discussions with
A.~Bailey, J.~Goodman, K.~Patra and V.~Van Eylen, and are
grateful to the people who have turned TESS from an idea into reality.
\added{L.G.B. thanks A.~Bixel and E.~May for clarifying details
concerning the available IMACS lightcurves.}
%
WASP-4 was included on the ``short-cadence'' target list thanks to the
Guest Investigator programs of J.\ Southworth and S.\ Kane (G011112
and G011183 respectively). 
%
J.N.W.\ thanks the TESS project and the Heising-Simons foundation for
supporting this work.
%
T.D. acknowledges support from MIT's Kavli Institute as a Kavli
postdoctoral fellow.
%
J.M.D. acknowledges funding from the European Research Council (ERC)
under the European Union's Horizon 2020 research and innovation
programme (grant agreement no. 679633; Exo-Atmos), and support from
the NWO TOP Grant Module 2 (Project Number 614.001.601).
%
J.E.R. was supported by the Harvard Future Faculty Leaders
Postdoctoral fellowship.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} 
  \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{radvel} \citep{fulton_radvel_2018},
  \texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
}

@@

We repeated all the data reduction and analysis steps described in
this paper for other hot Jupiters observed by TESS for which timing
data exists spanning many years.  First, we checked which hot Jupiters
were observed over the first three TESS sectors using a combination of
\texttt{tessmaps}\footnote{\url{github.com/lgbouma/tessmaps}, 
	commit \texttt{569bbc2}} and
TEPCat \citep{southworth_homogeneous_2011}.  We recalculated the
barycentric corrections using the \citet{eastman_achieving_2010} code,
and found values that agreed with the lightcurve headers to within
about 1 second.  We then selected hot Jupiters for which there were at
least five distinct epochs reported in the peer-reviewed literature.
We required that each observation be of a single transit, that the
midpoint be fit as a free parameter, and that the time system be
clearly documented.  Our final hot Jupiter sample included WASP-4b,
5b, 6b, 18b, and 46b.  The collected and measured times are given in
Tables~5, 6, 7, and 8 for each.
